Fivebranes

### 2022-03-14 fivebranes/index.tex
plethystic
e36char

The index we compute has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
  \item $r$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $q$ denotes a generator for the Cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}
These $U(1)$ weights are summarized in table \ref{tbl:weights1}.

@@

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- q^3 \frac{t_1 q^{-2} + t_1^{-1} t_2 q^{-2} + t_2^{-1} q^{-2} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
q^3 \frac{q^{-3}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on $K^{-1/2} \otimes \C^2$ contribute
\[
q^3 \frac{q^{-3/2} r + q^{-3/2}r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

@@

\begin{prop}
The character of local operators of the holomorphic twist of the theory on a single fivebrane is given by the following plethystic exponential
\[
{\rm PExp} \left[f_{tensor} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\[
f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{prop}

@@

Both characters break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
\[
q = r^2 , \quad t_2 = 1 .
\]
As one can easily check, this specialization yields the following single particle index
\[
f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{1}{1-q} 
\]
which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$.

\subsection{Character of E(3|6)}

>>>>

The index we compute has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
  \item $r$ denotes a generator for the Cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $q$ denotes a generator for the Cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}
These $U(1)$ weights are summarized in table \ref{tbl:weights1}.

@@

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
\[
q^{3/2}\frac{r + r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

@@

\begin{prop}
The character of local operators of the holomorphic twist of the theory on a single fivebrane is given by the following plethystic exponential
\[
{\rm PExp} \left[f_{tensor} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\[
f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{prop}

@@

Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
\beqn\label{eqn:special1}
q = r^2 , \quad t_2 = 1 .
\eeqn
As one can easily check, this specialization yields the following single particle index
\[
f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
\]
which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$.

\subsection{Character of $E(3|6)$}

Recall that the even part of $E(3|6)$ ...

\begin{itemize}
\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
\[
q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
\[
q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
\[
q^{3}\frac{q^{1/2} r + q^{1/2} r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

\begin{conj}
The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
\[
{\rm PExp} \left[f_{two} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\[
f_{two} (t_1,t_2,q,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{conj}

The specialization of this index in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
\]
which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.
